dbRDA analysis

### 2017-04-18 doc/RMD/RDA-analysis.Rmd
Add option to make wmn binary
This did not change the results of the analysis.

# function to gather Environmental variables, but averaging Severity
# (aka Straw Test, Virulence). This function is necessary because the
# data tends to randomly shuffle when being processed vai dplyr functions
# for better or for worse. ¯\_(ツ)_/¯
# 
# @param DAT the full data set
# @param CC The clone-corrected data set
# 
# @return A data frame containing Severity, Host, Source, Year, Region, and MLG
makeENV <- function(DAT, CC){
  # Creating the data frame with severity
  META   <- select(other(DAT)$meta, -Isolate)
  STRATA <- select(strata(DAT), -MCG)
  MLL    <- data.frame(MLG = mll(DAT))
  sev    <- bind_cols(META, STRATA, MLL) %>%
    group_by(Host, Source, Year, Region, MLG) %>% 
    summarize(Severity = mean(Severity)) %>% # Get mean severity per MLG
    ungroup()
  # Ensuring the data is in the correct order
  META   <- select(other(CC)$meta, -Isolate)
  STRATA <- select(strata(CC), -MCG)
  MLL    <- data.frame(MLG = mll(CC))
  bind_cols(META, STRATA, MLL) %>% 
    left_join(sev)
}

@@

>>>>

# function to gather Environmental variables, but averaging Severity
# (aka Straw Test, Virulence). This function is necessary because the
# data tends to randomly shuffle when being processed vai dplyr functions
# for better or for worse. ¯\_(ツ)_/¯
# 
# @param DAT the full data set
# @param CC The clone-corrected data set
# @param wmn should the "Source" column be converted to a binary wmn
#   factor? When this is true, everything that is not wmn will be converted
#   to "other"
# 
# @return A data frame containing Severity, Host, Source, Year, Region, and MLG
makeENV <- function(DAT, CC, wmn = FALSE){
  # Creating the data frame with severity
  META   <- select(other(DAT)$meta, -Isolate)
  STRATA <- select(strata(DAT), -MCG)
  STRATA <- if (wmn) mutate(STRATA, Source = ifelse(Source == "wmn", "wmn", "other")) else STRATA
  MLL    <- data.frame(MLG = mll(DAT))
  sev    <- bind_cols(META, STRATA, MLL) %>%
    group_by(Host, Source, Year, Region, MLG) %>% 
    summarize(Severity = mean(Severity)) %>% # Get mean severity per MLG
    ungroup()
  # Ensuring the data is in the correct order
  META   <- select(other(CC)$meta, -Isolate)
  STRATA <- select(strata(CC), -MCG)
  MLL    <- data.frame(MLG = mll(CC))
  bind_cols(META, STRATA, MLL) %>% 
    left_join(sev)
}

@@

```{r}
wmn11 <- seppop(dat11, ~Source)$wmn %>% setPop(~Region)
wmn11_sub <- popsub(wmn11, blacklist = character(0))
min_span_net <- bruvo.msn(wmn11_sub, replen = other(wmn11)$REPLEN, add = TRUE, loss = TRUE, showplot = FALSE, include.ties = TRUE)
set.seed(67)
plot_poppr_msn(wmn11,
               min_span_net,
               inds = "none",
               mlg = TRUE,
               gadj = 6,
               nodelab = 100,
               nodebase = 1.15,
               palette = funky,
               cutoff = (0.5/11)*3,
               quantiles = FALSE,
               beforecut = TRUE,
               layfun = igraph::layout_with_lgl)
```
